### 2020-05-24 system-model.tex
:art: Reconstruct channel model

\begin{section}{System Model}
	Consider an IRS-aided multiuser SISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation. The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a Time-Division Duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}. Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with the same reflection coefficients for all subbands. Since a deterministic multisine waveform can boost the energy transfer efficiency \cite{Clerckx2016a} and creates no interference to the information signal \cite{Clerckx2018b}, we use a superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, to maximize the rate-energy tradeoff. Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester. In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\alpha)$ and $\alpha$ respectively. Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$. The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots. In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design. Perfect synchronization is assumed among the three parties in both scenarios.

	\begin{subsection}{Transmit Signal}
		Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$).
		\begin{subsubsection} {Modulated Information Waveform}
			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ over subband $n$, which follows a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$. The transmit information signal at time $t$ is
			\begin{equation}\label{eq:x_I}
				x_{I}(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,n}\tilde{x}_{I,k,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I,k,n}=s_{I,k,n}e^{j\phi_{I,k,n}}$ collects the magnitude and phase of the information signal of user $k$ at frequency $n$. We further define the information waveform vector $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}]^T \in \mathbb{C}^{N{\times}1}$.
		\end{subsubsection}

@@

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R^H \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^H \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}^H=[\boldsymbol{h}_{R,1,n},\dots,\boldsymbol{h}_{R,K,n}]^H \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}^H=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^H \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \mathrm{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R^H\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		Define $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Phi}_n^H=\boldsymbol{H}_{R,n}^H\mathrm{diag}\left\{\boldsymbol{h}_{I,n}\right\} \in \mathbb{C}^{K \times L}$. Therefore, \ref{eq:h_n} rewrites as
		\begin{equation}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}
		\end{equation}
	\end{subsection}

>>>>

\begin{section}{System Model}
	Consider an IRS-aided multiuser SISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation. The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$). It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a Time-Division Duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}. Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with the same reflection coefficients for all subbands. Since a deterministic multisine waveform can boost the energy transfer efficiency \cite{Clerckx2016a} and creates no interference to the information signal \cite{Clerckx2018b}, we use a superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, to maximize the rate-energy tradeoff. Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester. In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\alpha)$ and $\alpha$ respectively. Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\alpha=1$ and wireless information transfer (WIT) with $\alpha=0$. The adjustment of $\alpha$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots. In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design. Perfect synchronization is assumed among the three parties in both scenarios.

	\begin{subsection}{Transmit Signal}
		\begin{subsubsection} {Modulated Information Waveform}
			Let $\tilde{x}_{I,k,n}$ be the information symbol of user $k$ ($k=1,\dots,K$) over subband $n$, which follows a capacity-achieving i.i.d. Circular Symmetric Complex Gaussian (CSCG) distribution $\tilde{x}_{I,k,n}\sim\mathcal{CN}(0,1)$. The transmit information signal at time $t$ is
			\begin{equation}\label{eq:x_I}
				x_{I}(t)=\Re\left\{\sum_{k=1}^K\sum_{n=1}^N{w_{I,n}\tilde{x}_{I,k,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I,k,n}=s_{I,k,n}e^{j\phi_{I,k,n}}$ collects the magnitude and phase of the information signal of user $k$ at frequency $n$. We further define the information waveform vector $\boldsymbol{w}_{I,k}=[w_{I,k,1},\dots,w_{I,k,N}]^T \in \mathbb{C}^{N{\times}1}$.
		\end{subsubsection}

@@

	\begin{subsection}{Composite Channel Model}
		Denote the frequency response of the AP-user $k$ direct link as $\boldsymbol{h}_{D,k}=[h_{D,k,1},\dots,h_{D,k,N}]^T \in \mathbb{C}^{N \times 1}$. Let $[\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}] \in \mathbb{C}^{L \times N}$ be the frequency response of AP-IRS incident channel, where $\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$ corresponds to the $n$-th incident channel. Similarly, let $[\boldsymbol{h}_{R,k,1},\dots,\boldsymbol{h}_{R,k,N}]^H \in \mathbb{C}^{N \times L}$ be the frequency response of IRS-user $k$ reflective channel, where $\boldsymbol{h}_{R,k,n}^H \in \mathbb{C}^{1 \times L}$ corresponds to the $n$-th reflective channel. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the received signal by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$ \footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\beta_l=1 \ \forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. On top of this, the IRS matrix is constructed by collecting the reflection coefficients onto the main diagonal entries as $\boldsymbol{\Theta} = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. The IRS-aided link can be modeled as a concatenation of the AP-IRS channel, IRS reflection, and IRS-user $k$ channel, which for user $k$ over subband $n$ is
		\begin{equation}\label{eq:h_{E,k,n}}
			h_{E,k,n} = \boldsymbol{h}_{R,k,n}^H \boldsymbol{\Theta} \boldsymbol{h}_{I,n} = \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
		\end{equation}
		where $\boldsymbol{v}_{k,n}^H \triangleq \boldsymbol{h}_{R,k,n}^H \mathrm{diag}(\boldsymbol{h}_{I,n}) \in \mathbb{C}^{1 \times L}$ and $\boldsymbol{\phi}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}] \in \mathbb{C}^{L \times 1}$. Both direct and extra link contributes to the corresponding composite channel as
		\begin{equation}
			h_{k,n} = h_{D,k,n} + \boldsymbol{v}_{k,n}^H \boldsymbol{\phi}
		\end{equation}
		Let $\boldsymbol{V}_k^H=[\boldsymbol{v}_{k,1},\dots,\boldsymbol{v}_{k,N}]^H \in \mathbb{C}^{N \times L}$, the extra link for user $k$ is $\boldsymbol{h}_{E,k}=[h_{E,k,1},\dots,h_{E,k,N}]^T=\boldsymbol{V}_k^H \boldsymbol{\phi} \in \mathbb{C}^{N \times 1}$. Therefore, the composite channel of user $k$ is
		\begin{equation}\label{eq:h_k}
			\boldsymbol{h}_k = \boldsymbol{h}_{D,k} + \boldsymbol{V}_k^H \boldsymbol{\phi}
		\end{equation}
	\end{subsection}
